---
title: "my-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

# mypackage

## Intro

This mypackage **R** package is one that we will be modifying in Math 3190. It starts out with four functions: `add()`, `ggraph()`, `hello()`, and `subtract()`. All of these are quite simple except the `ggraph()`, which depends on `ggplot2` and gives a quick way to create a scatter plot with two vectors. 

This package also includes the data set called `cranes`. This is a simple data set that contains information about the number of cranes at Aransas National Wildlife Refuge in Austwell, Texas by year from 1938 to 2016.

## Examples

```{r examples, echo = T, eval = T, fig.width=6,fig.height = 4}
library(mypackage)
add(100, 50) # Adds the two numbers and gives the output
subtract(100, 50) # Subtracts the second number from the first 
hello() # Gives the message "hello world"

# The following is an example for ggraph:
p <- ggraph(x = cranes$year, y = cranes$cranes) # Gives a simple scatter plot
p

# p is a ggplot object, so we can add onto it using ggplot functions
p + labs(x = "Year", y = "Number of Cranes", 
         title = "Number of Cranes at Aransas National Wildlife Refuge") +
  scale_y_continuous(breaks = seq(0, 350, by = 50)) +
  scale_x_continuous(breaks = seq(1940, 2010, by = 10))
```



# Other Vignette Info 

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))

